---
title: 'Peer-graded Assignment: R Markdown Presentation & Plotly'
author: "Subramanyan K P"
date: "11/05/2019"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


## Slide with Bullets

- Create a web page presentation using R Markdown that features a plot created with Plotly. Host your webpage on either GitHub Pages, RPubs, or NeoCities. Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly.For more details on authoring R presentations please visit <https://support.rstudio.com/hc/en-us/articles/200486468>.

- Does the web page feature a date and is this date less than two months before the date that you're grading this assignment?

- Is the web page a presentation and does it feature an interactive plot that appears to have been created with Plotly?

## Slide with R Output

```{r mtcars, echo = FALSE, warning=FALSE}
library(plotly)
summary(mtcars)
```

## Slide with Plot

```{r echo = TRUE, warning=FALSE}
plot_ly(data = mtcars, x=~mpg, y=~disp ,
        color = ~mpg , type = 'scatter', mode = 'markers')
```

